---
title: "R PART -2"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = F)
```

```{r}
# load packages to use 
library(dplyr)
library(ggplot2)
library(readr)
library(tidyr)
library(lattice)
```
# Exercise 2.3
## a
a) Generate the following samples and make for each of the four samples a normal QQ plot:
1. one sample of size 160 from the t-distribution with 3 degrees of freedom
2.  one sample of size 110 from the N(2,4) distribution, i.e. the variance is $\sigma^2=4$

3. one sample of size 180 from the exponential distribution with rate parameter 2;
4. one sample of size 100 from the uniform distribution on the interval [1, 4].

```{r fig.height=10,fig.width=12}
x_t_distributed <- rt(n=160,df=3)
x_norm <- rnorm(n=110,mean = 2,sd=4)
x_exp <- rexp(180,2)
x_unif <- runif(100,1,4)

x_t_df <- data.frame(x_t_distributed,label=rep("t_distributed_data",160))
x_norm_df <-data.frame(x_norm,label=rep("normal_distributed_data",110)) 
x_exp_df <- data.frame(x_exp,label=rep("exp_distributed_data",180))
x_unif_df <- data.frame(x_unif,label=rep("unif_distributed_data",100))

df <-x_t_df %>% bind_rows(x_norm_df) %>% bind_rows(x_unif_df) %>% bind_rows(x_exp_df) %>% 
  pivot_longer(cols = c(x_t_distributed,x_norm,x_unif,x_exp),names_to="distribution")

df %>% ggplot(aes(sample=value))+
  geom_qq(distribution = qnorm)+
  geom_qq_line()+
  facet_wrap(~label)+
  theme_minimal()+
  theme(strip.background.x = element_rect(fill = "black",
                                        linetype = "blank"),
        strip.text.x =element_text(face = "bold",
                                    color = "white", size = 14))
  
  
qqnorm(x_exp)


```
#b) 
Answer for each of the data sets below the following question: “Is it reasonable to assume
that the data come from a normal distribution?” In each case choose from the two answers:
“Obviously not from a normal distribution” or “Normality cannot be excluded”. Base your
answer on histograms, boxplots and normal QQ-plots.
Also, for each dataset, point out the peculiarities of each sample by comparing the histogram, boxplot, and QQ-plot with each other. Indicate whether you detect (some/all)
peculiarities in some/all of these diagnostic plots.


## 1. Titanic dataset
```{r fig.width=4,fig.height=4}

titanic_data <- read_csv("C:\\Users\\Chris\\Downloads\\phpMYEkMl.csv")

titanic_data$age %>% as.integer() %>% qqnorm(main="QQ PLOT FOR AGES OF PASSENGERS\n ABOARD THE TITANIC")
titanic_data$age %>% as.integer() %>%histogram(main="HISTOGRAM OF AGE OF\n PASSENGERS")
titanic_data$age %>% as.integer() %>% boxplot(main="BOXPLOT OF AGES OF\n PASSENGERS")

```
## Vlbw dataset 
```{r}
newborn <- read_csv('https://raw.githubusercontent.com/fonnesbeck/Bios8366/master/data/vlbw.csv')

newborn$bwt %>% qqnorm(main='NORMAL QQ PLOT FOR\n CHILD BIRTHWEIGHTS')
newborn$bwt %>%boxplot(main='BOX PLOT FOR\n CHILD BIRTHWEIGHTS')
newborn$bwt %>%histogram(main='HISTOGRAM OF  \n CHILD BIRTHWEIGHTS')
```


